Quantitative quality of lipid-cholesterol interactions in atomistic resolution molecular dynamics simulations

### 2017-02-01 MANUSCRIPT/manuscript.tex
Update form factor figure
Update simulation system information in the table
Update the table
Add rough draft of intro

%\label{}
\section{Introduction}
The quantitative quality of lipid-cholesterol interactions in atomistic resolution models will be determined against 
NMR and scattering data.

@@

CHARMM36\cite{klauda10,lim12}   & POPC   & 128& 0& 0\% & 5120  & 303  & 150 & 100 & [\citenum{charmm36files}]$^*$  &  [\citenum{botan15}]  \\
%                                & POPC   & 512& 0& 0\% & 23943  & 298  & 170 & 100 & [\citenum{charmmPOPC512files}]$^*$  & SI  \\
%                                & POPC   & 460& 52& 10\% & 23569  & 298  & 170 & 100 & [\citenum{charmmPOPC512files}]$^*$  & SI  \\
%                                & POPC   & 436& 76& 15\% & 23331  & 298  & 170 & 100 & [\citenum{charmmPOPC512files}]$^*$  & SI  \\
                                & POPC   & 100 & 24 & 19\%  &  4960   & 303 & 200 & 100 & [\citenum{charmm36files20perCHOL}]$^*$ & [\citenum{botan15}] \\
%                                & POPC   & 410& 102& 20\% & 20972  & 298  & 170 & 100 & [\citenum{charmmPOPC512files}]$^*$  & SI  \\
%                                & POPC   & 384& 128& 25\% & 22327  & 298  & 170 & 100 & [\citenum{charmmPOPC512files}]$^*$  & SI  \\
%                                & POPC   & 332& 180& 35\% & 21340  & 298  & 170 & 100 & [\citenum{charmmPOPC512files}]$^*$  & SI  \\
%                                & POPC   & 256& 256& 50\% & 20334  & 298  & 170 & 100 & [\citenum{charmmPOPC512files}]$^*$  & SI  \\
                               & POPC   & 80 & 80 &50\%  &  4496    & 303 & 200 & 100 & [\citenum{charmm36files50perCHOL}]$^*$ & [\citenum{botan15}] \\

@@

\section{Comparison of form factors between experiments and simulations}
The form factors calculated from different simulations with different cholesterol content are shown in 
Fig.~\ref{FormFactors}.

>>>>

%\label{}
\section{Introduction}
Importance of phospholipid cholesterol interactions in cellular membranes
have been reckognized for long time \cite{??}. Various ideas about 
lateral heterogeneities driven interactions between cholesterol, phosphatidylcholine
other other membrane lipids has been proposed \cite{??}. 
Especially coexistence of liquid-ordered and liquid-disordered phases
in PC-cholesterol mixtures has been suggested to be important in
biological lipid membranes \cite{??}.

Phase diagram of PC lipid cholesterol systems, including lo-ld coexistence
can be explained by simple models where cholesterol is assumed to 
induce order in neighboring lipids \cite{??}. This is important
achievement in order to understand biomembrane organization. 
However, also more detailed interactions driving interactions 
between cholesterol and other membrane lipid molecules are
often relevant. Several attempts to understand these interactions
have been made by using classical molecular dynamics simulations \cite{??}.
These simulations give atomistic resolution information, which not
directly accessible with any other techinique. However, 
the simulations often suffer from inaccuracies in force field
descriptions. Acyl chain region is usually well described in 
molecular dynamics simulation models, which is not the case for 
glycerol backbone and headgroup \cite{??}. 
The same applies to the systems with cholesterol. Practically all simulation
models qualitatively reproduce the condesing due to cholesterol, observed
as increase in acyl chain order parameters and decrease of area per molecule.
However, the some models significantly overestimate the changes in headgroup
due to the addition of cholesterol \cite{??}.

On the other hand, detailed analysis of lateral organization of 
lipid-cholesterol mixtures reveal significant differences between
different models. For example, significant angular organization
of lipids around cholesterol was observed in simulations with Berger
Höjtje models, while CHARMM36 simulations did not show such behaviour.

@@

CHARMM36\cite{klauda10,lim12}  & POPC   & 200& 0& 0\% & 9000  & 310  & ? & 100 & [\citenum{charmm36gromacs5chol0-30}]$^*$  &  SI   \\
                               & POPC   & 200& 22& 10\% & 9000  & 310  & ? & 100 & [\citenum{charmm36gromacs5chol0-30}]$^*$  &  SI   \\
                               & POPC   & 200& 50& 20\% & 9000  & 310  & ? & 100 & [\citenum{charmm36gromacs5chol0-30}]$^*$  &  SI   \\
                               & POPC   & 200& 86& 30\% & 9000  & 310  & ? & 100 & [\citenum{charmm36gromacs5chol0-30}]$^*$  &  SI   \\
                               & POPC   & 200& 134& 40\% & 15030  & 310  & ? & 100 & [\citenum{charmm36gromacs5chol40-50}]$^*$  &  SI   \\
                               & POPC   & 200& 200& 50\% & 18000  & 310  & ? & 100 & [\citenum{charmm36gromacs5chol40-50}]$^*$  &  SI   \\
Slipids\cite{jambeck12b,jambeck12,jambeck13b}  & POPC   & 200 & 0 & 0\%   & ?  & 310 & ? & 100 & [\citenum{slipidsCHOL0-30T310}]$^*$ & SI  \\
                                               & POPC   & 200 & 22 & 10\% & ?  & 310 & ? & 100 & [\citenum{slipidsCHOL0-30T310}]$^*$ & SI  \\
                                               & POPC   & 200 & 50 & 20\% & ?  & 310 & ? & 100 & [\citenum{slipidsCHOL0-30T310}]$^*$ & SI  \\
                                               & POPC   & 200 & 86 & 30\% & ?  & 310 & ? & 100 & [\citenum{slipidsCHOL0-30T310}]$^*$ & SI  \\
                                               & POPC   & ? & ? & 30\% & ?  & 298 & 170 & 100 & [\citenum{slipidsCHOL30T298}]$^*$ & SI  \\
                                               & POPC   & 200 & 134 & 40\% & ?  & 310 & ? & 100 & [\citenum{slipidsCHOL40-50T310}]$^*$ & SI  \\
                                               & POPC   & 200 & 200 & 50\% & ?  & 310 & ? & 100 & [\citenum{slipidsCHOL40-50T310}]$^*$ & SI  \\
                                               & POPC   & ?& ? & 50\% & ?  & 298 & 170 & 100 & [\citenum{slipidsCHOL50T298}]$^*$ & SI  \\ 

@@

\newpage
\section{Comparison of form factors between experiments and simulations}
The form factors calculated from different simulations with different cholesterol content are shown in 
Fig.~\ref{FormFactors}.
